DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-08-09 2015CompleteDerivation/completeDerivation.tex
Another pass at kinematic

\section{Kinematics and elementary systems}

We will now focus our attention to the simplest possible classical material: one for which the motion in space is necessary and sufficient to reconstruct the state and its evolution. That is, the internal dynamics can be ignored. What we'll find is that the dynamics of each infinitesimal part follows classical Lagrangian mechanics. Furthermore, the Hamiltonian of the system is constrained to the one of a free particles under scalar and vector potential forces.

@@

Here we make the link conceptually explicit with the following assumption:

@@

	The assumption clearly cannot be taken in general. Not all material will be elementary in the sense that they may have some internal dynamics. That is: position in space is not their only state variable. Yet, the assumption is fundamental because what we learn about the link between kinematic and dynamical quantities applies to all materials, even the non elementary ones.

	The first natural question to ask is: why do all systems have \emph{at least} to describe a trajectory in space? This seems motivated by the previous assumption of reducibility: spatial extent is the one way that all materials are reduced. Therefore the description of all particles of all materials, regardless of whether they are elementary or not, will include spatial degrees of freedom. Kinematic variables will form a set of independent degrees of freedom that are universal.

	When the system is not elementary, the particles will be described by the kinematic variables plus some additional independent state variables. Yet, the set of all possible evolutions will include those for which kinematic variables evolve independently from the other. For example, the evolutions for which the internal d.o.f. do not change. In other words: the overall dynamics will be the spatial degrees of freedom coupled with the internal degrees of freedom. Therefore by studying an elementary material, we are also studying a component of the dynamics that is present in all materials.

	It should be also noted that, once we reduced particles to be infinitesimal at a point, the rest of the description must be a local object invariant under coordinate transformations. This means that the remaining internal dynamics must be identified by scalar, vector or tensor quantities. This may be used in the future to justify the extension of this work to field theories.

	To be clear: we are not saying that kinematic equivalence is fundamental because everything must reduce to a material with no internal dynamics. While this statement seems reasonable and fits our physical intuition, we have no a priori argument for it. We can imagine, in fact, that as we reduce the behavior of one material to its constituents we find the parts to possess richer and richer states. For example, most macroscopic object are neutral though the parts are charged. We could imagine that, while dividing into parts, we find more and more types of charges, forces and internal dynamics. We do not have an argument why this cannot happen.

	What we are saying is that any classical material is \emph{at least} an elementary material and will have posses the dynamic of one coupled with the internal dynamics.
\end{rationale}

@@

As we need to describe trajectories, we introduce $\mathcal{M}$ as the $n+1$ dimensional manifold that defines space and time. A point in $\mathcal{M}$ will be identified by $x^\alpha = (t, x^i)$, its time and space coordinates. A trajectory will be given by a set of functions $x^\alpha(s)$ where $s$ is an arbitrary parametrization of the curve. What we need to understand is the link between the state space of all the possible trajectories and the complete state space of the particles of a classical material.

@@

Under the kinematic equivalence, given a trajectory we must identify a state and vice-versa. There must be a homeomorphism between the complete state space and the space of possible trajectories. We already know what the complete state space is. We just need to find a way to label the trajectories so that we can express the correspondence.

Because of the double role of $\mathcal{M}$, we can set half of our state variables to be equal to the space-time variables: $q^\alpha = (t, q^i) = x^\alpha$. This already tells us that the trajectory is differentiable since $q^i(t)$ is differentiable. The four velocity $u^\alpha = d_s x^\alpha$ is therefore well defined and it can be used to identify trajectories. The magnitude of the four velocity can be rescaled by changing the evolution parameter, $u^\alpha = d_s x^\alpha = d_s \hat{s} \, d_{\hat{s}} x^\alpha = d_s \hat{s} \, \hat{u}^\alpha$, and is therefore not physical. Only the direction is physical so the four velocity gives us another $n$ independent variables to identify trajectories. The combined position and velocity, which we call \emph{initial conditions}, identify $2n + 1$ trajectories using a hyper-surface of the tangent bundle $T\mathcal{M}$. This is exactly the dimensionality of the complete state space $\bar{\mathcal{S}} \subset T^*\mathcal{M}$. We cannot add more curves, as a homeomorphism preserves dimensionality, therefore we found the suitable space for the trajectories of particles of a classical material under the kinematic assumption.

Being able to identify particle through both state variables and initial conditions is not enough: we also need to be able to express the distributions of the composite states over position and velocity. As such, the differentiable distribution over state variables must become a differentiable distribution over initial condition. This tells us the transformation is differentiable.

@@

This relationship allows us to write the initial conditions in terms of the state variable. In particular we have $u^\alpha=u^\alpha(t, q^i, E, p_i)$. As the relationship is invertible, these functions must be monotonic in $E$ and $p_i$. Since $\partial_{p_i} \mathcal{H}=d_s q^i= u^i$ and $- \partial_{E} \mathcal{H}= d_s t= u^0$, $\mathcal{H}$ is convex in $E$ and $p_i$. Under such conditions we can define a Legendre transformation $\mathcal{L}=u^\alpha p_\alpha - \mathcal{H}$. Such transformation is the Lagrangian of the system and laws of motions are given by the Euler-Lagrange equation.

@@

Not only we must be able to express distributions in terms of both state variable and initial conditions, but integration has to carry over as well. To do that, we need to be able to count trajectories in the same way we are able to count states. There must exist a metric $g$, consistent with $\omega$, that allows to calculate the cardinality of possibilities for initial conditions. That is: $\omega(dt,dq^i,dE,dp_i) \propto g(dx^\alpha,du^\alpha)$.

@@

This also allows to give $c$ a more insightful physical meaning. It is not a velocity: the metric is defined at each point without motion. It is the constant of proportionality that maps a range of initial condition from the time variable $t$ to the space variable $x^i$. In the same way that $1$km would correspond to a thousand times more initial conditions than $1$m, $1$sec corresponds to $299,792,458$ more initial conditions than $1$m. Therefore when we write $x^\alpha = (ct, x^i)$ or $p_\alpha = (- E/c, p_i)$ we are really expressing everything in units that are proportional to the cardinality of state and possibilities. Naturally, these units make the book keeping of number of states much easier which, as we saw, is the only thing that Hamiltonian and Lagrangian mechanics are doing.

@@

The link between $\omega$ and $g$ allows us to constrain the kind of diffeomorphism between state variables and initial conditions. If we express the possibilities in terms of both state variables and initial conditions we have: $dq^\alpha \wedge dp_\alpha \propto dx^\alpha du_\alpha$. Since  $p_\alpha=p_\alpha(x, u)$, we have $dp_\alpha = m du_\alpha$, where $m$ is the constant of proportionality. We recognize $m$ as the inertial mass. Integrating the expression, we have $p_\alpha = m u_\alpha + A_\alpha(x)$ where $A_\alpha(x)$ is an arbitrary function. This is the most general link between velocity and conjugate momentum, which is the sum of kinetic momentum and a scalar potential.

@@

The above discussion gives the inertial mass a new physical meaning: it is the conversion constant that tells us how to convert a range of velocity to a range of conjugate momentum with the same number of possibilities. In other words: the more massive the particles, the more states per unit velocity. Intuitively, a more massive body is harder to accelerate because it has to go through more states for the same change in velocity. Note that the Hamiltonian excludes massless particles because the kinematic assumption does that implicitly. A massless particle always has the same velocity, $c$, therefore the trajectory is not enough to tell us the dynamics. The motion of the photon is not enough to tell us its energy or its momentum. Therefore it makes sense that, by assuming kinematic equivalence we implicitly required massive particles.

We have seen that the inertial mass $m$, the invariant speed $c$ and the reduced Plank constant $\hbar$ all serve the same purpose: convert one quantity to another preserving the number of possibilities. $dp=\hbar dk$ converts between ranges of wave number and conjugate momentum. $dx = c dt$ converts between ranges of time and space. $dp = m du$ converts between ranges of velocity and conjugate momentum. They allow to keep proper book keeping when mapping sets of states. Using natural units means measuring all these quantities through the cardinality of possibilities. There is a difference, though: while $c$ and $\hbar$ are simply determined by the unit system, $m$ also depends on the type of material. That is, different homogeneous materials can have different inertial mass.

@@

We should also ask whether any choice of $A$ actually represent a different case leading to different trajectories. The simplest and more insightful way to study this problem is to use $x^\alpha$ and $mu_\alpha$ as state variable. They are not going to be conjugates of each other but they do capture the entire physical description. Any change in $A$ that does not affect the relationship between $x^\alpha$ and $mu_\alpha$ does not change the physics. Expressing the Hamiltonian and the Poisson brackets in terms of the initial conditions we have:
\begin{align*}
\mathcal{H}&=\frac{1}{2m}(mu_\alpha mu^\alpha + m^2 c^2) \\
\{x^\alpha, x^\beta\} &= 0 \\
\{x^\alpha, mu_\beta\} &= \delta^\alpha_\beta \\
\{mu_\alpha, mu_\beta\} &= \partial_\alpha A_\beta - \partial_\beta A_\alpha = F_{\alpha\beta}
\end{align*}
Note how the Poisson bracket between kinetic momentum is the force tensor. The weaker the force, the more $(x^i, mu_i)$ become independent d.o.f. The force tensor, then, tells how much $(x^i, mu_i)$ fail to be independent d.o.f.. With these expressions, the commutator between any function of position and kinetic momentum can now be calculated. For example:
\begin{align*}
d_s x^\alpha &= \{x^\alpha, \mathcal{H}\} = u^\alpha \\
d_s (mu^\alpha) &= \{mu^\alpha, \mathcal{H}\} = F^{\alpha\beta} u_\beta
\end{align*}
where we recognize the covariant form of the Lorentz force.

Any change of $A$ that leaves $F_{\alpha\beta}$ unchanged does not affect the motion of any function of position and velocity. Such transformation is what we call a gauge transformation. Note the same group of transformations is found by fixing $A$ and changing $p$ such that the laws of motion don't change. In other words: $A$ and $p$ are defined relatively to the each other. $A$ defines the $0$ for $p$ and vice versa. The gauge group expresses the arbitrariness of such definition.

The extended Hamiltonian we found is quadratic in energy, therefore negative energy states are possible. These correspond to the particle anti-states mentioned in \ref{antistates}. As we fixed the natural parametrization, $u^\alpha u_\alpha = - c^2$, there are two cases: the parametrization is aligned with time, therefore $s=\tau$ where $\tau$ is proper time, or the parametrization is anti-aligned with time, therefore $s=-\tau$. The trajectory velocity $u^\alpha= \pm d_\tau x^\alpha$ is plus or minus the physical velocity depending on whether it's a standard particle state or an anti-state. Expanding the equation for the force, we have:
\begin{align*}
\pm d_\tau (\pm m d_\tau x^\alpha) &= m d_\tau^2 x^\alpha = \pm  F^\alpha_\beta d_\tau x^\beta
\end{align*}
Therefore the force act on anti-particle states in the opposite way: they act as if they have opposite charge. Note that nothing physical is actually going backwards in time, just the parametrization.

In this setting, charge conjugation $C$ is simply changing the parametrization from $s$ to $-s$, following the trajectories in the opposite way. This will permute each particle anti-state with the corresponding standard state and vice-versa. But if we apply parity $P$ and time reversal $T$, changing $x^\alpha$ to $-x^\alpha$, we would have the same net effect: the parametrization stays the same, but it now moves backwards in space and time. As they have the same net effect, if we apply all three we go back where we started. This gives us a very intuitive classical particle mechanics analogue for the $CPT$ theorem.

To sum up, the kinematic assumption has more inherent consequences one would expect at first. It means the particles are identified by position and velocity and therefore the system of equation is second order. It links the space of initial conditions on $T\mathcal{M}$ with the space of states on $T^*\mathcal{M}$. Such link allows state space metric $\omega$ to induce the space-time metric $g$. It allows us to define Lagrangians. It constrains the motion to massive particles under scalar and vector potential forces. Moreover, it allowed to re-understand basic concepts, like the invariant speed $c$, the inertial mass $m$ and the force tensor $F_{\alpha\beta}$ in terms of state counting and d.o.f. independence.

We now have all the building block of classical mechanics, the consequences of three seemingly simple assumption. But that's not all: we have also placed ourselves in a very good position to move forward to quantum systems by using the new physical insights we have gained.

@@

>>>>

\section{Kinematics and minimal materials}

We will now focus our attention to the simplest possible classical material: one that is fully described by its motion in space, the internal dynamics can be ignored. What we'll find is that the dynamics of each infinitesimal part follows classical Lagrangian mechanics. Furthermore, the Hamiltonian of the system is constrained to the one of a free particles under scalar and vector potential forces.

@@

Our aim is to make that link more conceptually crisp and explicit with the following assumption:

@@

	The assumption clearly cannot be taken in general: kinematic variables may not fully identify the particle state of a material. Yet, the assumption is fundamental because particles of any material will \emph{at least} describe a trajectory in space and what we learn about the link between kinematic and dynamical quantities applies to all materials, even the ones where the kinematic assumption does not apply.

	The first natural question to ask is: why does state evolution always describe a trajectory in space? Because spatial extent is the one way that all materials can be decomposed. As we divide materials in smaller pieces, physical location is one of the state variable for the particles of all materials. If we assume kinematic equivalence, the kinematic variables will be enough to identify a particle state. In such a case, we will call the material \emph{minimal} to highlight the idea that the state is described by the smallest possible number of d.o.f..

	When the system is not minimal, the particles will be described by some additional independent state variables. The overall dynamics will be the spatial d.o.f. coupled with the internal d.o.f.. Therefore by studying a minimal material, we are also studying a component of the dynamics that is present in all materials.

	To be clear: we are not saying that kinematic equivalence is fundamental because everything must reduce to a material with no internal dynamics. That is: we are not saying elementary materials are minimal. While this statement seems reasonable and may fit our physical intuition, we have no a priori argument for it. We can imagine, in fact, that as we reduce the behavior of one material to its constituents we find the parts to possess richer and richer states. In a similar way that the elementary particles have electromagnetic and color charges, while their aggregation is typically neutral, we could imagine finding more and more richness in the internal dynamics. While this does not seem to happen in practice, we do not have an argument why this cannot happen.

	What we are saying is that any material is \emph{at least} a minimal material and will possess the dynamic of one coupled with the internal dynamics.

	It should also be noted that, once we reduced particles to be infinitesimal at a point, the rest of the description must be a local object invariant under coordinate transformations. This means that the remaining internal dynamics must be identified by scalar, vector or tensor quantities. This may be used in the future to justify the extension of this work to field theories. 
\end{rationale}

@@

As we need to describe trajectories, we introduce $\mathcal{M}$ as the $n+1$ dimensional manifold that defines space and time. A point in $\mathcal{M}$ will be identified by $x^\alpha = (t, x^i)$, its time and space coordinates. A trajectory will be given by a set of functions $x^\alpha(s)$ where $s$ is an arbitrary parametrization of the curve. What we need to understand is the link between the complete state space of the particles of a classical material and the space of all the possible trajectories under the kinematic assumption.

@@

Under kinematic equivalence, given a trajectory we must identify a state and vice-versa. There must be a homeomorphism between the complete state space and the space of possible trajectories. We already know what the complete state space is. We just need to find a way to label the trajectories so that we can express the correspondence.

Because of the double role of $\mathcal{M}$, we can set half of our state variables to be equal to the space-time variables: $q^\alpha = (t, q^i) = x^\alpha$. This already tells us that the trajectory is differentiable since $q^i(t)$ is differentiable. The four velocity $u^\alpha = d_s x^\alpha$ is therefore well defined and it can be used to identify trajectories. The magnitude of the four velocity can be rescaled by changing the evolution parameter, $u^\alpha = d_s x^\alpha = d_s \hat{s} \, d_{\hat{s}} x^\alpha = d_s \hat{s} \, \hat{u}^\alpha$, and is therefore not physical. Only the direction is physical so the four velocity gives us another $n$ independent variables to identify trajectories. The combined position and velocity, the kinematic variables, identify $2n + 1$ trajectories using a hyper-surface of the tangent bundle $T\mathcal{M}$. This is exactly the dimensionality of the complete state space $\bar{\mathcal{S}} \subset T^*\mathcal{M}$. We cannot add more curves, as a homeomorphism preserves dimensionality, therefore we found the suitable space for the trajectories of particles of a classical material under kinematic equivalence.

Being able to identify particles through either state or kinematic variables is not enough: we also need to be able to express the distributions of the composite states over position and velocity. As such, the differentiable distribution over state variables must become a differentiable distribution over kinematic variables. This tells us the transformation is differentiable.

@@

This relationship allows us to write the kinematic variables in terms of the state variable. In particular we have $u^\alpha=u^\alpha(t, q^i, E, p_i)$. As the relationship is invertible, these functions must be monotonic in $E$ and $p_i$. Since $\partial_{p_i} \mathcal{H}=d_s q^i= u^i$ and $- \partial_{E} \mathcal{H}= d_s t= u^0$, $\mathcal{H}$ is convex in $E$ and $p_i$. Under such conditions we can define a Legendre transformation $\mathcal{L}=u^\alpha p_\alpha - \mathcal{H}$. Such transformation is the Lagrangian of the system and laws of motions are given by the Euler-Lagrange equation.

@@

\begin{justification}
	We claim $\mathcal{H}$ is convex in $E$ and $p_i$. By \ref{initial_conditions} we can write the velocity $u^\alpha=u^\alpha(q^\alpha, E, p_i)$ as a differentiable function of the state variables. At fixed $q^\alpha$, $u^\alpha$ must be invertible. $u^\alpha$ are monotonic in $E$ and $p_i$. $\partial_{p_i} \mathcal{H}=d_s q^i= u^i$ and $- \partial_{E} \mathcal{H}= d_s t= u^0$. The derivatives of $\mathcal{H}$ in $E$ and $p_i$ are monotonic in $E$ and $p_i$. $\mathcal{H}$ is convex in $E$ and $p_i$.

	We claim there exist a Lagrangian $\mathcal{L}=u^\alpha p_\alpha - \mathcal{H}$. $\mathcal{H}$ is convex in $E$ and $p_i$. It admits a Legendre transform. The Lagrangian $\mathcal{L}$ is such transform.
\end{justification}

Not only we must be able to express distributions in terms of both state and kinematic variables, but integration has to carry over as well. To do that, we need to be able to count trajectories in the same way we are able to count states. There must exist a metric $g$, consistent with $\omega$, that allows to calculate the cardinality of possibilities for initial conditions. That is: $\omega(dt,dq^i,dE,dp_i) \propto g(dx^\alpha,du^\alpha)$.

@@

This also allows to give $c$ a more insightful physical meaning. It is not a velocity: the metric is defined at each point without motion. It is the constant of proportionality that maps a range of initial conditions from the time variable $t$ to the space variable $x^i$. In the same way that $1$km would correspond to a thousand times more possible states than $1$m, $1$sec corresponds to $299,792,458$ more possible states than $1$m. Therefore when we write $x^\alpha = (ct, x^i)$ or $p_\alpha = (- E/c, p_i)$ we are really expressing everything in units that are proportional to the cardinality of state and possibilities. Naturally, these units make the book keeping of number of states much easier which, as we saw, is the only thing that Hamiltonian and Lagrangian mechanics are doing.

@@

The link between $\omega$ and $g$ allows us to constrain the kind of diffeomorphism between state variables and kinematic variables. If we express the possibilities in terms of both state variables and initial conditions we have: $dq^\alpha \wedge dp_\alpha \propto dx^\alpha du_\alpha$. Since  $p_\alpha=p_\alpha(x, u)$, we have $dp_\alpha = m du_\alpha$, where $m$ is the constant of proportionality. We recognize $m$ as the inertial mass. Integrating the expression, we have $p_\alpha = m u_\alpha + A_\alpha(x)$ where $A_\alpha(x)$ is an arbitrary function. This is the most general link between velocity and conjugate momentum, which is the sum of kinetic momentum and a scalar potential.

@@

The above discussion gives the inertial mass a new physical meaning: it is the conversion constant that tells us how to convert a range of velocity to a range of conjugate momentum with the same number of possibilities. In other words: the more massive the particles, the more states per unit velocity. Intuitively, a more massive body is harder to accelerate because it has to go through more states for the same change in velocity. Note that the Hamiltonian excludes massless particles because the kinematic assumption does that implicitly. A massless particle always has the same velocity, $c$, therefore the trajectory is not enough to tell us the dynamics. The motion of the photon is not enough to tell us its energy or its momentum. Therefore it makes sense that, by assuming kinematic equivalence we derived equation valid only for massive particles.

We have seen that the inertial mass $m$, the invariant speed $c$ and the reduced Plank constant $\hbar$ all serve the similar purposes: convert one quantity to another preserving the number of possibilities. $dp=\hbar dk$ converts between ranges of wave number and conjugate momentum. $dx = c dt$ converts between ranges of time and space. $dp = m du$ converts between ranges of velocity and conjugate momentum. They allow to keep proper book keeping when mapping sets of states. Using natural units means measuring all these quantities through the cardinality of possibilities. There is a difference, though: while $c$ and $\hbar$ are simply determined by the unit system, $m$ also depends on the type of material. That is, different homogeneous materials can have different inertial mass.

@@

We should also ask whether any choice of $A$ actually represent a different case leading to different trajectories. The simplest and more insightful way to study this problem is to use the kinematic quantities $x^\alpha$ and $mu_\alpha$ as state variable. They are not going to be conjugates of each other but they do capture the entire physical description. Any change in $A$ that does not affect the relationship between $x^\alpha$ and $mu_\alpha$ does not change the physics. Expressing the Hamiltonian and the Poisson brackets in terms of the initial conditions we have:
\begin{align*}
\mathcal{H}&=\frac{1}{2m}(mu_\alpha mu^\alpha + m^2 c^2) \\
\{x^\alpha, x^\beta\} &= 0 \\
\{x^\alpha, mu_\beta\} &= \delta^\alpha_\beta \\
\{mu_\alpha, mu_\beta\} &= \partial_\alpha A_\beta - \partial_\beta A_\alpha = F_{\alpha\beta}
\end{align*}
Note how the Poisson bracket between kinetic momentum is the force tensor. The weaker the force, the more $(x^i, mu_i)$ become independent d.o.f. The force tensor, then, tells how much $(x^i, mu_i)$ fail to be independent d.o.f.. With these expressions, the commutator between any function of position and kinetic momentum can now be calculated. For example:
\begin{align*}
d_s x^\alpha &= \{x^\alpha, \mathcal{H}\} = u^\alpha \\
d_s (mu^\alpha) &= \{mu^\alpha, \mathcal{H}\} = F^{\alpha\beta} u_\beta
\end{align*}
where we recognize the covariant form of the Lorentz force.

Any change of $A$ that leaves $F_{\alpha\beta}$ unchanged does not affect the evolution of any function of position and velocity. Such transformation is what we call a gauge transformation. Note the same group of transformations is found by fixing $A$ and changing $p$ such that the laws of motion don't change. In other words: $A$ and $p$ are defined relatively to the each other. $A$ defines the $0$ for $p$ and vice versa. The gauge group expresses the arbitrariness of such definition.

The extended Hamiltonian we found is quadratic in energy, therefore negative energy states are possible. These correspond to the particle anti-states mentioned in \ref{antistates}. As we fixed the natural parametrization, $u^\alpha u_\alpha = - c^2$, there are two cases: the parametrization is aligned with time, therefore $s=\tau$ where $\tau$ is proper time, or the parametrization is anti-aligned with time, therefore $s=-\tau$. The trajectory velocity $u^\alpha= \pm d_\tau x^\alpha$ is plus or minus the physical velocity depending on whether it's a standard particle state or an anti-state. Expanding the equation for the force, we have:
\begin{align*}
\pm d_\tau (\pm m d_\tau x^\alpha) &= m d_\tau^2 x^\alpha = \pm  F^\alpha_\beta d_\tau x^\beta
\end{align*}
Therefore the force acts on anti-particle states in the opposite way: they act as if they have opposite charge. Note that nothing physical is actually going backwards in time, just the parametrization.

In this setting, charge conjugation $C$ is simply changing the parametrization from $s$ to $-s$. This will permute particle standard and anti-state as they follow the trajectories in the opposite direction. But if we apply parity $P$ and time reversal $T$, changing $x^\alpha$ to $-x^\alpha$, we would have the same net effect: the parametrization stays the same, but it now moves backwards in space and time. As they have the same net effect, if we apply all three we go back where we started. This gives us a very intuitive classical particle mechanics analogue for the $CPT$ theorem.

To sum up, the kinematic assumption has more inherent consequences one would expect at first. It means the particles are identified by position and velocity and therefore the system of equations is second order. It links the space of trajectories on $T\mathcal{M}$ with the space of states on $T^*\mathcal{M}$. Such link allows state space metric $\omega$ to induce the space-time metric $g$. It allows us to define Lagrangians. It constrains the motion to massive particles under scalar and vector potential forces. Moreover, it allowed to re-understand basic concepts, like the invariant speed $c$, the inertial mass $m$ and the force tensor $F_{\alpha\beta}$ in terms of state counting possibilities and d.o.f. independence.

We now have all the building block of classical mechanics, the consequences of three seemingly simple assumption. We have more insight of why these blocks fit together the way they do. But we have also placed ourselves in a very good position to move forward to quantum systems by using the new physical insights we have gained.

@@

In principle, we should be able to simply introduce assumption \ref{???} and work our way to quantum mechanics. Unfortunately, given that all sorts of things have been said on quantum system, as well as their opposites, it is best to spend some time clarifying our take on some of these matters. This will decrease the chance of being misconstrued later.

We will spend this section talking about the similarities between classical and quantum system. We will see that classical distributions already possess qualitative properties that are typically associated with quantum systems. Therefore it is more natural to think of quantum systems, to a first approximation, as composite states then particle states. This will allow us in the next chapter to truly pinpoint how and why classical and quantum systems are different.

\subsection{Particles and distributions (waves)}

The core problem of much confusion for quantum system is identifying them as something akin to classical particles. This alone leads
